---
title: "Alert data - Updated with reverse coding"
author: "Kevin"
date: "3/30/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
# Independent variables factors, plots and scores
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#all needed libraries for factor analysis
library(tinytex)
library(MASS)
library(car)
library(GPArotation)
library(psych)
library(tidyverse)
library(haven)
library(lme4)
library(knitr)


```



```{r Alert data, echo=FALSE, warning=FALSE, message=FALSE}
#data cleaning
raw_check <- read_csv("/Users/kkwiley/alert_0328.csv")


raw_check[raw_check == 11] <- NA
raw_check <- lapply(raw_check, as.numeric)#changing from string to numeric
raw_check <- as.data.frame(raw_check)

#reverse coding questions 11
raw_check$q11 <- 6 - raw_check$q11
raw_check$q11[raw_check$q11 == 0] <- 6

#reverse coding questions 12
raw_check$q12 <- 6 - raw_check$q12
raw_check$q12[raw_check$q12 == 0] <- 6

#reverse coding questions 20
raw_check$q20 <- 6 - raw_check$q20
raw_check$q20[raw_check$q20 == 0] <- 6

#reverse coding questions 21
raw_check$q21 <- 6 - raw_check$q21
raw_check$q21[raw_check$q21 == 0] <- 6

#reverse coding questions 53
raw_check$q53 <- 6 - raw_check$q53
raw_check$q53[raw_check$q53 == 0] <- 6

#reverse coding questions 55
raw_check$q55 <- 6 - raw_check$q55
raw_check$q55[raw_check$q55 == 0] <- 6

#reverse coding questions 56
raw_check$q56 <- 6 - raw_check$q56
raw_check$q56[raw_check$q56 == 0] <- 6

#reverse coding questions 57
raw_check$q57 <- 6 - raw_check$q57
raw_check$q57[raw_check$q57 == 0] <- 6

```


```{r independent variables, echo=FALSE, warning=FALSE}
#scree plot with independent variables
ch_aw_alert_scree <- fa.parallel(raw_check[c(6:30, 89:93)], fm = 'minres', fa = 'fa')

#analysis with print outs of factor loadings
ch_raw_loadings_IV <- fa(raw_check[c(6:30, 89:93)], nfactors=5, rotate = "oblimin", fm="minres")

print(ch_raw_loadings_IV)
print(ch_raw_loadings_IV$loadings,cutoff = 0.3)

#diagram
fa.diagram(ch_raw_loadings_IV)
```


# Dependent variable factors, plots and scores

```{r DVs for factors, echo=FALSE, warning=FALSE}
#scree plot with independent variables
ch_DVraw_alert_scree <- fa.parallel(raw_check[31:40], fm = 'minres', fa = 'fa')

#analysis with print outs of factor loadings
ch_DVraw_loadings <- fa(raw_check[31:40], nfactors=2, rotate = "oblimin", fm="minres")

print(ch_DVraw_loadings)
print(ch_DVraw_loadings$loadings,cutoff = 0.3)

#diagram
fa.diagram(ch_DVraw_loadings)

#combining scores to dataset

ch_raw_scores_IV <- ch_raw_loadings_IV$scores#creating scores dataset from IV scores
ch_raw_scores_DV <- ch_DVraw_loadings$scores#creating scores dataset from DV scores
ch_raw_alert2 <- cbind(ch_raw_scores_IV, ch_raw_scores_DV)#combining DV and IV scores

ch_raw_alert_final <- cbind(raw_check, ch_raw_alert2)#combining for final dataset
#changing variable names
colnames(ch_raw_alert_final)[113] <- "Staff_percep"
colnames(ch_raw_alert_final)[114] <- "Perc_org_cap"
colnames(ch_raw_alert_final)[115] <- "Sup_pol_proc"
colnames(ch_raw_alert_final)[116] <- "Consent_proc"
colnames(ch_raw_alert_final)[117] <- "Per_event_notcap"
colnames(ch_raw_alert_final)[118] <- "Care_qual"
colnames(ch_raw_alert_final)[119] <- "Care_coord"

alert_0330 <- ch_raw_alert_final

```




### Regressions are run with only one independent variable 

###Care Quality regressed on Staff Perceptions

```{r regression analyses - IV1, echo=FALSE}

raw_lm <- lm(Care_qual ~ Staff_percep, data = alert_0330)
summary(raw_lm)
```

### Care Quality regressed on Perceived Organizational Capacity
```{r regression analyses - IV2, echo=FALSE}

raw_lm2 <- lm(Care_qual ~ Perc_org_cap, data = alert_0330)
summary(raw_lm2)
```
### Care Quality regressed on Supportive Policies and Procedures
```{r regression analyses - IV3, echo=FALSE}

raw_lm3 <- lm(Care_qual ~ Sup_pol_proc, data = alert_0330)
summary(raw_lm3)
```
### Care Quality regressed on Consent procedures
```{r regression analyses - IV4, echo=FALSE}

raw_lm4 <- lm(Care_qual ~ Consent_proc, data = alert_0330)
summary(raw_lm4)
```
### Care Quality regressed on Percived event notification capacity
```{r regression analyses - IV5, echo=FALSE}

raw_lm5 <- lm(Care_qual ~ Per_event_notcap, data = alert_0330)
summary(raw_lm5)
```

### Care Coordination regressed on Staff perceptions
```{r regression analyses - DV2 & IV1, echo=FALSE}

lmd1 <- lm(Care_coord ~ Staff_percep, data = alert_0330)
summary(lmd1)
```
### Care Coordination regressed on Perceived Organizational Capacity
```{r regression analyses - DV2 & IV2, echo=FALSE}

lmd2 <- lm(Care_coord ~ Perc_org_cap, data = alert_0330)
summary(lmd2)
```
### Care Coordination regressed on Supportive Policies and Procedures
```{r regression analyses - Care_Coord & IV3, echo=FALSE}

lmd3 <- lm(Care_coord ~ Sup_pol_proc, data = alert_0330)
summary(lmd3)
```
### Care Coordination regressed on Consent Procedures
```{r regression analyses - Care_Coord & IV4, echo=FALSE}

lmd4 <- lm(Care_coord ~ Consent_proc, data = alert_0330)
summary(lmd4)
```
### Care Coordination regressed on Perceived Event Notification Capacity
```{r regression analyses - DV2 & IV5, echo=FALSE}

lmd5 <- lm(Care_coord ~ Per_event_notcap, data = alert_0330)
summary(lmd5)
```

#Random effects regression clustering on organization - Care Quality
```{r}
###GLMM mixsed effects model
re_glm <- lmer(Care_qual ~ Staff_percep + Perc_org_cap + Sup_pol_proc + Consent_proc + Per_event_notcap  + (1| org_id) + (1 | QE), data = alert_0330)
summary(re_glm)

```
#random effects and pvalues for Care Quality

```{r}
# extract coefficients
coefs <- data.frame(coef(summary(re_glm)))
# use normal distribution to approximate p-value
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
format(round(coefs, 4))
```

#Random effects regression clustering on organization - Care Coordination
```{r}
#Random effects regression clustering on organization
###GLMM mixsed effects model
re_glm2 <- lmer(Care_coord ~ Staff_percep + Perc_org_cap + Sup_pol_proc + Consent_proc + Per_event_notcap + (1| org_id) + (1 | QE) , data = alert_0330)
summary(re_glm2)
```

#random effects and pvalues for Care Coordination
```{r}
#random effects and pvalues for DV2
# extract coefficients
coefs2 <- data.frame(coef(summary(re_glm2)))
# use normal distribution to approximate p-value
coefs2$p.z <- 2 * (1 - pnorm(abs(coefs2$t.value)))
format(round(coefs2, 4))
```





